Cryptographic assurance of fairness in voting

### 2012-11-16 proposal/proposal.tex
Rewrite things, kill the mostly-redundant abstract

% setup
\documentclass[10pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{color}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{listings}
\usepackage{array}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{multicol}

@@

% title
\title{Cryptographic techniques to ensure fair elections}
\date{}
\author{
\begin{tabular}{c c c}
Kelsey Francis & Curtis Free & Christopher Martin \\
\small \tt{francis@gatech.edu} & \small \tt{curtis.free@gatech.edu} & \small \tt{chris.martin@gatech.edu}
\end{tabular}
}

@@

	\begin{abstract}
		Current election processes do not allow participants to verify the accuracy of vote counting.
		Applied cryptography research has yielded a number of candidate systems to replace or accompany
		voting existing voting procedures to provide fairness guarantees while maintaining ballot secrecy.
		We will define a set of security properties sufficient to make an election both ``fair'' and ``secret'',
		survey existing literature on the matter, and -- if time permits -- produce a proof-of-concept
		implementation of a system that meets these goals (either the best system we find, or one of
		our own creation using borrowed techniques).
	\end{abstract}
	\begin{multicols}{2}

@@

			Fairness of elections is of vital importance to nations such as the United States in which
			government officials are elected to office by the people.

			But how often is this fairness challenged? Given voting systems widely used today, citizens
			must trust that the government (a) counts all cast votes (correctly) and (b) counts
			\emph{only} votes actually cast.

			Researchers have proposed a variety of systems that make use of cryptography to empower the
			people to verify in an election that one or both of those requirements has been met by the
			body performing the election -- with the crucial stipulation that this verification allows
			individual ballots to remain secret.

		\section{Proposal}

			Our project will accomplish three goals.

			\subsection{Specification of security goals}

				We plan to begin by defining what requirements we believe must be met in order for an
				election to be considered ``fair'' and translating those requirements into precise security
				goals that we can reason about using cryptographic techniques. (For example, at what points
				in the election should we require authenticated encryption, and what are the appropriate
				unforgeability constraints?)

			\subsection{Literature survey}

				We will then study existing literature on the subject, paying close attention to existing
				end-to-end auditable voting systems, including both in-person systems (our primary focus)
				such as Scantegrity \cite{scantegrity} and Pr\^{e}t \`{a} Voter \cite{preta} and online
				voting systems that attempt to meet the same goals such as Helios \cite{helios}.

			\subsection{Proof-of-concept implementation}

				Having surveyed prior research, and time-permitting, we will consider the extent to which
				previously-developed systems meet our requirements and construct a proof-of-concept
				implementation of one such system or one of our own design, using borrowed techniques in
				an attempt to meet all the goals we set forth.

@@

% vim: set colorcolumn=101 cursorcolumn cursorline:

>>>>

% setup
\documentclass[10pt]{article}
\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{multicol}

@@

% title
\title{Cryptographic assurance of fairness in voting}
\date{}
\author{
\begin{tabular}{c c c}
Kelsey Francis & Curtis Free & Christopher Martin \\
\small \tt{francis@gatech.edu} & \small \tt{curtis.free@gatech.edu} & \small \tt{chris.martin@gatech.edu}
\end{tabular}
}

@@

\thispagestyle{empty}

\begin{multicols}{2}

@@

Citizens' ability to trust the fairness of elections is vital to governments whose rule
is subject to the consent of the governed, but it is not uncommon for the veracity of
election results to come into question.
Current election processes do not allow participants to verify the accuracy of vote counting.

Problems such as identity fraud and equality of ballot access are not amenable to
cryptographic solutions, but their propensity to be externally observable limits the
potential for widespread abuse.
Internal manipulation by the government conducting the poll is a more insidious threat,
and it is here where we may fruitfully apply cryptography to ensure honesty.
Research in this field has yielded a number of candidate systems to replace or accompany
existing voting procedures to provide fairness guarantees while maintaining ballot secrecy.

% But how often is this fairness challenged? Given voting systems widely used today, citizens
% must trust that the government (a) counts all cast votes (correctly) and (b) counts
% \emph{only} votes actually cast.

% Researchers have proposed a variety of systems that make use of cryptography to empower the
% people to verify in an election that one or both of those requirements has been met by the
% body performing the election -- with the crucial stipulation that this verification allows
% individual ballots to remain secret.

\section{Security goals}

We will formulate a precise security definitions of requirements we believe
must be met  in a ``fair'' and ``private'' election.

Fairness requires that enough information is published such that anyone is able to
independently tabulate results, and a receipt given to each voter provides evidence
of fraud in the event that the voter's ballot is miscounted.

Ballot secrecy is a constraint that most cryptography applications do not require.
When votes are counted correctly, a voter must not be able to prove any
facts about the ballot that was cast.

\section{Literature survey}

We will then study existing literature on the subject, paying close attention to existing
end-to-end auditable voting systems.
Our primary focus is in-person systems such as Scantegrity \cite{scantegrity} and
Pr\^{e}t \`{a} Voter \cite{preta}.
We also consider online voting systems such as Helios \cite{helios}.

\section{Proof of concept}

If time permits, we will construct a proof-of-concept implementation of a system that meets
our goals, based on the systems described in the literature if they are sufficient.

@@
